

<!-- THIS RMARDOWN FILE CONTAINS INITIALIZATION OF SERIES OF ELEMENTS FOR THE REPORT
     IT ALSO DISPLAY IN THE REPORT DETAILS ON THE RUNNING ENVIRONMENT
     
     DO NOT MODIFY THIS FILE IF YOU ARE NOT A RMARKDWON EXPERT
-->


<!-- Javascript for zooming on figures (adapted from: https://stackoverflow.com/questions/40401680) -->
<!-- Jquery import conflicts with DT::datatable so needs to be commented here -->
<!-- <script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script> -->

<style>
.zoomDiv {
  display: none;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  background-color: #FFFFFF;
  box-shadow: 0px 0px 50px #888888;
  width: fit-content;
  max-width: 90%;
  max-height: 90%;
  overflow: auto;
}

.zoomImg {
  width: 100%;
}
</style>

<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick for all img except the zoomed one and link ones (filter)
    // use 'img.zoom' and out.extra='class=\"zoom\"' in chunk to specify manually which chunk images can be zoomed
    $('img:not(.zoomImg)').filter(':not(a *)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').show();
    });
    // onClick function for hiding div
    $('img.zoomImg').click(function() {
      $('.zoomDiv').hide();
    });
  });
</script>




```{r rmd_initFunctions}

### Create output directory
dir.create( PATH_ANALYSIS_OUTPUT, showWarnings = FALSE);


### Record starting time (for report and file names)
startTime = Sys.time();
startTimeReport   = format( startTime, "%Y %m %d %H:%M:%S")
startTimeFileName = format( startTime, "%Y_%m_%d_%H_%M_%S")


### Initialize utils

# Create a hash for all parameters
paramsHash = digest( environment(), algo="murmur32");

# Create a hidden plotly in a tagList to allow using them in loops later
cat('<div style="display: none">');
htmltools::tagList(plotly::plot_ly(x = rnorm(10), type = "histogram"))
cat('</div>');

# Same for datatable....
cat('<div style="display: none">');
datatable( data.frame(a=1:10, b = 1:10),
           class = "compact",
           filter="top",
           rownames = FALSE,
           #colnames = ,
           #caption = ,
           extensions = c('Buttons', 'Select'))
cat('</div>');

```


---
title: `r paste( GLOBAL_DESCRIPTION, ANALYSIS_STEP_NAME, sep ="<BR>")`
---


## Run informations {.tabset .tabset-fade}

### Run
<center>
```{r rmd_runInfo_run}
pander( c( 'Date'     = startTimeReport,
           'Sample'   = EXPERIMENT_NAME,
           'Hash'     = paramsHash));
```
</center>

### Parameters
```{r rmd_runInfo_params}
listParams = as.list( paramsEnv);
pander(listParams[order(names(listParams))]); # Show params in alphabetical order
```

### System
<center>
```{r rmd_runInfo_sysInfo}
showSimpleDT( Sys.info())
```
</center>

### R
```{r rmd_runInfo_r}
pander( sessionInfo());
```

<!-- Ending the tabset section -->
<!-- ## {.toc-ignore} -->
<br /><br />
